DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
space

In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent
$A(z)$, while $y$ represents the synthesized stable digital controller,
which is defined by Eq.(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}

>>>>

In Fig.~\ref{toolbox-usage}, ``num'' represents $B(z)$ and ``den'' represent
$A(z)$, while $y$ represents the synthesized stable digital controller,
which is defined by Eq.~(\ref{equation_controller}).
%
\begin{equation}
\label{equation_controller}
C(z)=\frac{-0.9983^{2}+0.09587z+0.1926}{z^2+0.5665z+0.75}.
\end{equation}
